GEEPERs: Principal Stratification using Principal Scores and Stacked Estimating Equations

### 2022-09-15 writeUps/paper.tex
GEEPERs

\title{GEEPERS: Principal Stratification using Principal Scores and Stacked Estimating Equations}

@@

In a separate, if related, line of research, \citet{ding2011}, \citet{jiangDing2021}, and others have shown that, under certain circumstances, researchers can use baseline covariates to identify and estimate principal effects without relying on principal ignorability.
This paper expands on those identification results by presenting a new set of principal effect estimators, and associated standard error estimates, based on a generalized estimating equations (or M-estimation or method-of-moments) \citep{stefanskiBoos}.
It turns out that, under certain general conditions, principal effects can be estimated with a simple, two-step procedure: first, estimate principal scores with logistic regression or another M-estimator; then, impute unknown principal subroup membership indicators with principal scores and estimate principal effects using OLS with interactions, just as in the pre-treatment subgroup case.

We refer to the estimators presented here as ``GEEPERs'': generalized estimating equations for principal effects using regressions.

@@

\section{GEEPERS}

@@

We begin by introducing an assumption that we term ``Covariate Ignorability,'' or CI.
\begin{ass}[Covariate Ignorability]\label{ass:ci}
\begin{equation}\label{eq:assumption}
\EE[\yci|\bxsi,\sti]=\EE[\yci|\sti]=\muc0\text{ or }\muc1
\end{equation}
\end{ass}
i.e. $Y_C$ is mean-independent of $\bxs$ conditional on $\st$.
Under CI, covariates are not informative of the mean of $Y_C$ within principal strata.
As stated above, CI will rarely be plausible.
However, in some circumstances researchers can identify a subset of observed covariates that satisfy CI, and use those covariates in estimation.

@@

Thus, given principal scores, Assumption \ref{ass:ci} enables an analyst to estimate principal effects with a simple regression.
If principal scores were known exactly, the M-estimation structure of $\hat{\eff0}$ and $\hat{\eff1}$ implies that their sampling variance could be estimated by the standard sandwich estimator for OLS \citep{sefanskiBoosArticle}.
This will rarely be the case.
However, if the principal scores are modeled as \eqref{eq:prinScoreMod}, and parameters $\bm{\alpha}$ are estimated by M-estimation, with estimating equations $\sum_{i: Z_i=1}\Omega_i=\bm{0}$, then the estimating equations for the principal score model and principal effect estimation can be stacked \citep[c.f.][]{boosStefanskiBook}, as
\begin{equation}\label{eq:stacked}
  \sum_{i=1}^n \begin{pmatrix}
    Z_i\Omega_i(\bxsi,S_i;\bm{\alpha})\\
    \Psi_i\left(Y_i,Z_i,\ri(\bm{\alpha}); \bm{\beta}\right)\end{pmatrix}=\begin{pmatrix} \bm{0}\\\bm{0}\end{pmatrix}
\end{equation}
where $\ri\left(\bm{\alpha}\right)=S_iZ_i+\ppip{\bm{\alpha}}$ emphasizes $\ppi$'s dependence on $\bm{\alpha}$.
In practice, the principal score model \eqref{eq:prinScoreMod} could be fit first, yielding estimates $\bm{\hat{\alpha}}$, and model \eqref{eq:regression0} could be fit next, using $\ri=\ri\left(\bm{\hat{\alpha}}\right)$.
Together, the vector of estimates $[\bm{\hat{\alpha}},\bm{\hat{\beta}}]$ represents a zero of the stacked estimating equations \eqref{eq:stacked}.

@@

\subsection{Relaxing Covariate Ignorability with Outcome Modeling}
In most applications, identifying a set of covariates $\bxs$ satisfying CI will be difficult or impossible.
Fortunately, CI may be relaxed or obviated by regression.
Let $\bxy\in \mathbb{R}^k$, be a vector of covariates (possibly the same as $\bxs$); $\bxy$ can contain transformations and interactions of baseline covariates, allowing for a wide range of models.
Then note that $\st$ is, essentially, a covariate, so by randomization, (Assumption \ref{ass:rand}), $\EE[\bxy|\st]=\EE[\bxy|\st,Z=0]=\EE[\bxy|\st,Z=1]$.
Then information about the stratum-specific means of $\bxy$ can be extrapolated from the treatment to the control group.
This leads to the following proposition:
\begin{prop}\label{prop:interactions}
  Say
  \begin{equation}\label{eq:interaction}
    \begin{split}
      Y_{Ci}=\beta_0^C+\bm{\beta_1}^{C'}\bxy_i+\beta_2^C\sti+\bm{\beta_3^{C'}}\bxy_i\sti+\epsilon_{Ci}\\
      Y_{Ti}=\beta_0^T+\bm{\beta_1}^{T'}\bxy_i+\beta_2^T\sti+\bm{\beta_3^{T'}}\bxy_i\sti+\epsilon_{Ti}\\
    \end{split}
  %  \end{equation}
%      +\beta_3Z_i+\beta_4\sti Z_i+\bm{\beta_5}'\bxy_i\sti+
 %   \bm{\beta_6}'\bxy Z_i+\bm{\beta_7}'\bxy_i Z_i\sti+
  \end{equation}
  with $\EE[\epsilon_i]=0$ and $\{Z_i,\sti,\bxy_i\}\independent \epsilon_i$.
  Then say the following model is fit with OLS
  \begin{equation}\label{eq:fullInteractionModel}
    Y_i=\beta_0+\bm{\beta_1}'\bxy_i+\beta_2\ri+\beta_3Z_i+\beta_4\ri Z_i+\bm{\beta_5}'\bxy_i\ri+
    \bm{\beta_6}'\bxy Z_i+\bm{\beta_7}'\bxy_i Z_i\ri+\epsilon_i
  \end{equation}
  with $\ri$ as defined in \eqref{eq:ri},
  yielding coefficient estimates $\hat{\beta}_k$, $k=0,\dots,3$.
  Then
   \begin{equation}\label{eq:prinEffEst}
  \begin{split}
    \hat{\eff0}_{int}&\equiv \hat{\beta}_3+\bm{\beta}_6'\overline{\bxy}_{Z=1,S=0}\\
    \hat{\eff1}_{int}&\equiv \hat{\beta}_3+(\bm{\hat{\beta}_6}+\bm{\hat{\beta}_7})'\overline{\bxy}_{Z=1,S=1}
  \end{split}
\end{equation}
   are M-estimators, with $\hat{\eff0}_{int}\rightarrow_p\eff0$ and $\hat{\eff1}_{int}\rightarrow_p\eff1$ as $n\rightarrow\infty$,
   where $\overline{\bxy}_{Z=1,S=s}$ is a vector of the $k$ column means of the rows of $\bxy$ corresponding to subjects with $Z=1$ and $S=s$.
\end{prop}

@@

Fortunately, simpler models can be fit much more efficiently. In particular, if interactions between covariates and treatment assignment are omitted, then data from the treatment group---in which $\st$ is fully observed---can be used to estimate the coefficients on covariates.
Such a model implies a fairly strong assumption, that the only interactions between covariates and treatment assignment are due to differences between principal effects.
However, there are two mitigating points.
First, since there is no requirement that all relevant covariates be included in the model, a researcher can exclude covariates from a model if he or she thinks their relationship with $Y$ may vary substantially between treatment groups, even in the same principal stratum.
Second, simulation results in the next section suggest that some models excluding important interactions may still yield reliable inferences.

As in the simpler case discussed in \S~\ref{sec:ci}, since the estimators in \eqref{eq:prinEffEst} are M-Estimators, their sampling variance can be estimated with a consistent sandwich estimator.
Uncertainty in principal score estimation can be incorporated by stacking the estimating equations for the principal score model \eqref{eq:prinScoreMod} and estimating the combined covariance matrix \eqref{eq:sandwich}..

@@

We conducted a simulation study to compare the performance of our regression estimator compared to a Bayesian mixture model and to a principal score weighting estimator, in both favorable and unfavorable circumstances.
The study was designed to answer three sets of overarching questions.
First, how does the performance of the M-estimator vary as sample size and the extent to which $\bx$ predicts $\st$, and the principal effects themselves vary, and when important interactions were omitted from the outcome model.
Second, how does the M-estimator could compete with the mixture model? Is it competitive in circumstances favorable to both techniques? Does it avoid the pitfalls of mixture modeling when the parametric assumptions of the normal mixture model fail?
Third, are there ways or circumstances when the principal score weighting estimator outperforms the M-estimator even though principal ignorability does not hold?

@@

Across simulation runs, there were $n=500$ subjects in each treatment arm.

Given three indpendent standard normal covariates, $x_k$ $k=1,\dots,3$,
principal scores were simulated as
\begin{equation*}
  \ppi=logit^{-1}\left[\alpha(x_{1i}+x_{2i}+x_{3i})\right]
\end{equation*}
where $\alpha$ is a manipuated factor.
When $\alpha$ was higher, $\st$ was more easily predicted by covariates; when $\alpha=0$, Assumption \ref{ass:vps}, was violated, i.e. $Var(\ppi)=0$.

@@

In most simulation runs, there were no interactions between
Control potential outcomes were generated as
\begin{equation}\label{eq:yc-sim}
  \yci=\beta_1(x_{1i}+x_{2i})+[\muc1+\beta_2(x_{1i}+x_{2i})]\sti +x_{3i}/\sqrt{6}+\epsilon_i
\end{equation}
where $\EE[\epsilon_i]=0$ $Var(\epsilon_i)=1/2$, and the distribution of $\epsilon_i$ and $\muc1$ were manipulated factors in the study.
In most simulations, there was no interaction between $\st$ and $x_1$ and $x_2$; in those cases, $\beta_1=1/\sqrt{6}$, and $\beta_2=0$.
In simulation runs including an interaction with $\st$, $\beta_1=3/(4\sqrt{6})$ and $\beta_2=5/(4\sqrt{6})$.

@@

@@

For the purpose of demonstrating GEEPERS, we gathered dichotomized data on %which students in the treatment condition requested at least one bottom-out hint.
whether students in the treatment condition requested more than the median number of bottom-out hints (11).
That is, $\st=1$ for students who, if assigned to the treatment condition, would request at more than 11 bottom-out hints (``bottom-outers''), and $\st=0$ for students who would request 11 or fewer (``non-bottom-outers''). %least one bottom-out hint, and $\st=0$ for students who would not.
The outcome of interest $Y$ in our example is students' total scores on a ten-item posttest completed within the online tutoring system; $Y$ is an integer ranging from 0 to 10.
The goal of our analysis will be to determine the principal effects $\tau_1=\EE[\yt-\yc|\st=0]$ and $\tau_0=\EE[\yt-\yc|\st=0]$, the average effects of assignment to the treatment condition for bottom-outers and non-bottom-outers.

@@

The data analysis we present here is intended as a demonstration of GEEPERS, rather than for its substantive conclusions, and our description omits discussion of some important methodological considerations, including attrition and post-selection inference. For a more complete discussion of the experimental design, the conditions being compared, and the impact analysis, please see \citet{impactPaper}.

\subsection{Principal Score Model}

@@

\subsection{Outcome Regression and Principal Effects}
\begin{figure}
  \centering
  \includegraphics{../figure/prinEffs.pdf}
  \caption{Principal Effects}
  \label{fig:effects}
\end{figure}

@@

>>>>

\title{GEEPERs: Principal Stratification using Principal Scores and Stacked Estimating Equations}

@@

In a separate, if related, line of research, \citet{jo2002}, \citet{ding2011}, \citet{jiangDing2021}, and others have shown that, under certain circumstances, researchers can use baseline covariates to identify and estimate principal effects without relying on principal ignorability.
This paper expands on those identification results by presenting a new set of principal effect estimators, and associated standard error estimates, based on a generalized estimating equations (or M-estimation or method-of-moments) \citep{stefanskiBoos}.
It turns out that, under certain general conditions, principal effects can be estimated with a simple, two-step procedure: first, estimate principal scores with logistic regression or another M-estimator; then, impute unknown principal subroup membership indicators with principal scores and estimate principal effects using OLS with interactions, just as in the pre-treatment subgroup case.
We will refer to the estimators presented here as ``GEEPERs'': generalized estimating equations for principal effects using regressions.
GEEPERs estimates rely on correct specification of regression functions, but unlike common fully-parametric methods, they make no assumptions about the distribution of regression errors.
Unlike principal score weighting, GEEPERs does not assume principal ignorability, and admits to sandwich-style standard error estimates, which we provide in the appendix.

This paper focuses on a special case of principal stratification---one-way, binary non-compliance---that is, there are only two principal strata, and principal stratum membership is observable in one treatment arm, but not in the other.
This scenario would occur if, say, subjects in the control arm of a study had no access to the treatment, and not all subjects assigned to the treatment arm actually received the full treatment.
While such a setup may represent the simpliest and easiest principal stratification problem, we believe it is a common scenario.
Moreover, we believe that the methods developed here can extend to more complex scenarios, which we leave to future work.

The following section gives a formal introduction to principal stratification and briefly describes two common estimation techniques, parametric mixture modeling and principal score weighting.
Next, section \ref{sec:geepers} develops GEEPERs estimation, and gives conditions for its consistency.
Section \ref{sec:simulation} describes a simulation study examining the operating characteristics of GEEPERs estimates and comparing them to estimates from parametric mixture modeling and principal score weighting.
Under ideal circumstances, estimates from parametric mixture models and weighting estimators are somewhat more efficient than GEEPERs, but when assumptions are violated GEEPERs easily out-performs the other two methods.
Section \ref{sec:fh2t} illustrates GEEPERs in analyzing data from a recent large-scale field trial of educational software, and Section \ref{sec:discussion} concludes.

@@

\section{GEEPERs}\label{sec:geepers}

@@

We begin by introducing an assumption that we term ``Covariate Ignorability,'' or CI. It is a slighty weaker version of \citet{jiangDing2021}'s ``auxilliary indpendence'' assumption.
\begin{ass}[Covariate Ignorability]\label{ass:ci}
\begin{equation}\label{eq:assumption}
\EE[\yci|\bxsi,\sti]=\EE[\yci|\sti]=\muc0\text{ or }\muc1
\end{equation}
\end{ass}
i.e. $Y_C$ is mean-independent of $\bxs$ conditional on $\st$.
Under CI, covariates are not informative of the mean of $Y_C$ within principal strata.
As stated above, CI will rarely be plausible.
However, in some circumstances researchers can identify a subset of observed covariates that satisfy CI, and use those covariates in estimation.

@@

Thus, given principal scores, Assumption \ref{ass:ci} enables an analyst to estimate principal effects with a simple regression.
Proposition \ref{prop:reg1} builds on Theorem 2 of \citet{jiangDing2021} which establishes identification of $\eff0$ and $\eff1$ by representing the principal effect estimators as a familiar regression using estimated principal scores.

If principal scores were known exactly, the M-estimation structure of $\hat{\eff0}$ and $\hat{\eff1}$ implies that their sampling variance could be estimated by the standard sandwich estimator for OLS \citep{sefanskiBoosArticle}.
This will rarely be the case.
However, if the principal scores are modeled as \eqref{eq:prinScoreMod}, and parameters $\bm{\alpha}$ are estimated by M-estimation, with estimating equations $\sum_{i: Z_i=1}\Omega_i=\bm{0}$, then the estimating equations for the principal score model and principal effect estimation can be stacked \citep[c.f.][]{boosStefanskiBook}, as
\begin{equation}\label{eq:stacked}
  \sum_{i=1}^n \begin{pmatrix}
    Z_i\Omega_i(\bxsi,S_i;\bm{\alpha})\\
    \Psi_i\left(Y_i,Z_i,\ri(\bm{\alpha}); \bm{\beta}\right)\end{pmatrix}=\begin{pmatrix} \bm{0}\\\bm{0}\end{pmatrix}
\end{equation}
where $\ri\left(\bm{\alpha}\right)=S_iZ_i+\ppip{\bm{\alpha}}$ emphasizes $\ppi$'s dependence on $\bm{\alpha}$.
In practice, the principal score model \eqref{eq:prinScoreMod} could be fit first, yielding estimates $\bm{\hat{\alpha}}$, and model \eqref{eq:regression0} could be fit next, using $\ri=\ri\left(\bm{\hat{\alpha}}\right)$.
Together, the vector of estimates $[\bm{\hat{\alpha}},\bm{\hat{\beta}}]$ represents a zero of the stacked estimating equations \eqref{eq:stacked}.

@@

\subsection{Relaxing Covariate Ignorability with Outcome Modeling}
In most applications, identifying a set of covariates $\bxs$ satisfying CI will be difficult or impossible.
Fortunately, CI may be relaxed or obviated by regression.
Let $\bxy\in \mathbb{R}^k$, be a vector of covariates (possibly the same as $\bxs$); $\bxy$ can contain transformations and interactions of baseline covariates, allowing for a wide range of models.
Then note that $\st$ is, essentially, a covariate, so by randomization, (Assumption \ref{ass:rand}), $\EE[\bxy|\st]=\EE[\bxy|\st,Z=0]=\EE[\bxy|\st,Z=1]$.
Then information about the stratum-specific means of $\bxy$ can be extrapolated from the treatment to the control group.
This leads to the following proposition:
\begin{prop}\label{prop:interactions}
  Say
  \begin{equation}\label{eq:interaction}
    \begin{split}
      Y_{Ci}=\beta_0^C+\bm{\beta_1}^{C'}\bxy_i+\beta_2^C\sti+\bm{\beta_3^{C'}}\bxy_i\sti+\epsilon_{Ci}\\
      Y_{Ti}=\beta_0^T+\bm{\beta_1}^{T'}\bxy_i+\beta_2^T\sti+\bm{\beta_3^{T'}}\bxy_i\sti+\epsilon_{Ti}\\
    \end{split}
  %  \end{equation}
%      +\beta_3Z_i+\beta_4\sti Z_i+\bm{\beta_5}'\bxy_i\sti+
 %   \bm{\beta_6}'\bxy Z_i+\bm{\beta_7}'\bxy_i Z_i\sti+
  \end{equation}
  with $\EE[\epsilon_i]=0$, $\{Z_i,\sti,\bxy_i\}\independent \epsilon_i$.
  Say $\ppi$ linearly independent of $\bxy$, and
  that the following model is fit with OLS
  \begin{equation}\label{eq:fullInteractionModel}
    Y_i=\beta_0+\bm{\beta_1}'\bxy_i+\beta_2\ri+\beta_3Z_i+\beta_4\ri Z_i+\bm{\beta_5}'\bxy_i\ri+
    \bm{\beta_6}'\bxy Z_i+\bm{\beta_7}'\bxy_i Z_i\ri+\epsilon_i
  \end{equation}
  with $\ri$ as defined in \eqref{eq:ri},
  yielding coefficient estimates $\hat{\beta}_k$, $k=0,\dots,3$.
  Then
   \begin{equation}\label{eq:prinEffEst}
  \begin{split}
    \hat{\eff0}_{int}&\equiv \hat{\beta}_3+\bm{\beta}_6'\overline{\bxy}_{Z=1,S=0}\\
    \hat{\eff1}_{int}&\equiv \hat{\beta}_3+(\bm{\hat{\beta}_6}+\bm{\hat{\beta}_7})'\overline{\bxy}_{Z=1,S=1}
  \end{split}
\end{equation}
   are M-estimators, with $\hat{\eff0}_{int}\rightarrow_p\eff0$ and $\hat{\eff1}_{int}\rightarrow_p\eff1$ as $n\rightarrow\infty$,
   where $\overline{\bxy}_{Z=1,S=s}$ is a vector of the $k$ column means of the rows of $\bxy$ corresponding to subjects with $Z=1$ and $S=s$.
\end{prop}

@@

Fortunately, simpler models can be fit much more efficiently. In particular, if interactions between covariates and treatment assignment are omitted, then data from the treatment group---in which $\st$ is fully observed---can be used to estimate the coefficients on covariates.
Such a model relies on what \citet{bo2002} calls ``Additivity of Treatment Assignment Effect,'' that $\bm{\beta_1}^{C}=\bm{\beta_1}^{T}$.
In other words, the only interactions between covariates and treatment assignment are due to differences between principal effects---a fairly strong assumpton.
However, there are two mitigating points.
First, since there is no requirement that all relevant covariates be included in the model, a researcher can exclude covariates from a model if he or she thinks their relationship with $Y$ may vary substantially between treatment groups, even in the same principal stratum.
Second, simulation results in the next section suggest that some models excluding important interactions may still yield reliable inferences.

As in the simpler case discussed in \S~\ref{sec:ci}, since the estimators in \eqref{eq:prinEffEst} are M-Estimators, their sampling variance can be estimated with a consistent sandwich estimator.
Uncertainty in principal score estimation can be incorporated by stacking the estimating equations for the principal score model \eqref{eq:prinScoreMod} and estimating the combined covariance matrix \eqref{eq:sandwich}, formulas for which are given in the appendix.

@@

We conducted a simulation study to compare the performance of GEEPERs compared to a Bayesian mixture model and to a principal score weighting estimator, in both favorable and unfavorable circumstances.
The study was designed to answer three sets of overarching questions.
First, how does the performance of the GEEPERs estimator vary under different conditions, including sample size, the extent to which $\bx$ predicts $\st$, the principal effects themselves vary, and when important interactions were omitted from the outcome model.
Second, how does GEEPERs compare with mixture modeling? Is it competitive in circumstances favorable to both techniques? Does it avoid the pitfalls of mixture modeling when the parametric assumptions of the normal mixture model fail?
Third, are there ways or circumstances when the principal score weighting estimator outperforms GEEPERs even though principal ignorability does not hold?

@@

In each run of the simulation, we simulated three indpendent standard normal covariates, $x_k$ $k=1,\dots,3$. However, only the first two covariates were ``observed,'' i.e. were included in the analysis model.
Given the covariates, the (true) principal scores were defined as
\begin{equation*}
  \ppi=logit^{-1}\left[\alpha(x_{1i}+x_{2i}+x_{3i})\right]
\end{equation*}
where $\alpha$ is a manipuated factor.
When $\alpha$ was higher, $\st$ was more easily predicted by covariates; when $\alpha=0$, Assumption \ref{ass:vps}, was violated, i.e. $Var(\ppi)=0$.

@@

Finally, potential outcomes were generated as in \eqref{eq:interaction}, with $\bxy=[\bm{x_1},\bm{x_2},\bm{x_3}]$,
and with $\EE[\epsilon_i]=0$ and $Var(\epsilon_i)=1/2$.
Across simulation runs, intercepts $\beta_0^C=\beta_0^T=0$ and the coefficient on the unobserved covariate $x_3$, $\beta_{1,3}^C=\beta_{1,3}^T= 1/\sqrt{6}$.
The distribution of $\epsilon_i$ and other coefficients $\bm{\beta}$ were manipulated factors in the study.

@@

In most simulations, there was no interaction between $\st$ and $x_1$ and $x_2$; in those cases, $\beta_1=1/\sqrt{6}$, and $\beta_2=0$.
In simulation runs including an interaction with $\st$, $\beta_1=3/(4\sqrt{6})$ and $\beta_2=5/(4\sqrt{6})$.

@@

For the purpose of demonstrating GEEPERs, we gathered dichotomized data on %which students in the treatment condition requested at least one bottom-out hint.
whether students in the treatment condition requested more than the median number of bottom-out hints (11).
That is, $\st=1$ for students who, if assigned to the treatment condition, would request at more than 11 bottom-out hints (``bottom-outers''), and $\st=0$ for students who would request 11 or fewer (``non-bottom-outers''). %least one bottom-out hint, and $\st=0$ for students who would not.
The outcome of interest $Y$ in our example is students' total scores on a ten-item posttest completed within the online tutoring system; $Y$ is an integer ranging from 0 to 10.
The goal of our analysis will be to determine the principal effects $\tau_1=\EE[\yt-\yc|\st=0]$ and $\tau_0=\EE[\yt-\yc|\st=0]$, the average effects of assignment to the treatment condition for bottom-outers and non-bottom-outers.

@@

The data analysis we present here is intended as a demonstration of GEEPERs, rather than for its substantive conclusions, and our description omits discussion of some important methodological considerations, including attrition and post-selection inference. For a more complete discussion of the experimental design, the conditions being compared, and the impact analysis, please see \citet{impactPaper}.

\subsection{Principal Score Model}\label{sec:psMod}

@@

\subsection{Outcome Regression and Principal Effects}\label{sec:outMod}
\begin{figure}
  \centering
  \includegraphics{../figure/prinEffs.pdf}
  \caption{Principal Effects}
  \label{fig:effects}
\end{figure}

@@

Figure \ref{fig:compare} shows principal effect estimates from GEEPERs (without the $S$-interactions) compared to analogous estimates using Bayesian mixture modeling and PSW.
All three sets of estimates relied on the same principal score model described above, in Section \ref{sec:psMod}, though in the mixture model it was fit simultaneously with effect estimation using a Markov Chain Monte Carlo algorithm \citep{rstan}.
The Bayesian mixture model assumed that outcomes were normally distributed, conditional on covariates (the same as in Section \ref{sec:outMod}) and principal stratum, with a residual standard deviation that varied between principal strata. This modeling assumption is necessarily false, since post-test scores were integers between 0 and 10. All model parameters with support in $\mathbb{R}$ were given standard normal priors, while standard deviation parameters were given half-standard normal priors.
The PSW estimators did not include any covariate outcome modeling. Standard errors for the PSW estimates were estimated using the bootstrap, with resamping done within schools.
For all three sets of estimators, approximate 95\% confidence intervals were estimated by subtracting twice the standard error from the point estimate (or twice the posterior standard deviation from the posterior mean, in the Bayesian mixture model).

In this case, all three estimation strategies largely agreed. This may suggest that the estimators' various assumptions---additivity of treatment assignment effect for GEEPERs and the mixture model, normal residuals for the mixture model, and principal ignorability for PSW---were all innocuous and may have held approximately. Alternatively, violations of the different assumptions may have led to similar errors.
